### 2022-07-11 paper/akweury/document.tex
update albedoGated model

\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

@@

The decomposition gives a constraint of the normal map with given other information, which can be considered further in the deep learning model. The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map.

L->L0L

>>>>

\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

@@

The decomposition gives a constraint of the normal map with given other information, which can be considered further in the deep learning model. The image $ I $ is given in the RGB-D image, the light map $ \textbf{L} $ can be calculated based on the light source and the vertex map. Since the brightness $ L_0 $ of the image is not take into account when we calculate the surface normal, it is save to remove it in the equation. Using the predicted surface normal map $  \bm{\hat{N}} $, then the calculated albedo $ \hat\rho $ is as follows
\[ \hat\rho = \frac{I}{\textbf{L} \cdot  \bm{\hat{N}} }  \]
The accuracy of $ \hat\rho $ is related to the accuracy of $  \bm{\hat{N}} $. The normal

V -> N
don't known albedo
L, N

N->rho
